\co{Enhanced tunability in ferroelectric composites through local field enhancement and the effect of disorder}

### 2019-09-27 paper/marked_manuscript.tex
theo

\documentclass[%
 aip,
% jmp,
% bmf,
% sd,
% rsi,
 amsmath,amssymb,
%preprint,%
 reprint,%
]{revtex4-1}

@@

%
% \usepackage{xcolor}
% \definecolor{correction}{HTML}{de5e5e}
\newcommand{\co}[1]{#1}

%
% \usepackage[outdir=./]{epstopdf}
% \graphicspath{{./}{../../data/figures/}}

@@

% \bibliographystyle{RS}
% \bibliography{biblio}

%merlin.mbs aipnum4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
%Control: key (0)
%Control: author (8) initials jnrlst
%Control: editor formatted (1) identically to author
%Control: production of article title (0) allowed
%Control: page (1) range
%Control: year (1) truncated
%Control: production of eprint (0) enabled
\begin{thebibliography}{36}%
\makeatletter
\providecommand \@ifxundefined [1]{%
 \@ifx{#1\undefined}
}%
\providecommand \@ifnum [1]{%
 \ifnum #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \@ifx [1]{%
 \ifx #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \natexlab [1]{#1}%
\providecommand \enquote  [1]{``#1''}%
\providecommand \bibnamefont  [1]{#1}%
\providecommand \bibfnamefont [1]{#1}%
\providecommand \citenamefont [1]{#1}%
\providecommand \href@noop [0]{\@secondoftwo}%
\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
\providecommand \@href[1]{\@@startlink{#1}\@@href}%
\providecommand \@@href[1]{\endgroup#1\@@endlink}%
\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
\providecommand \@@startlink[1]{}%
\providecommand \@@endlink[0]{}%
\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
\providecommand \urlprefix  [0]{URL }%
\providecommand \Eprint [0]{\href }%
\providecommand \doibase [0]{http://dx.doi.org/}%
\providecommand \selectlanguage [0]{\@gobble}%
\providecommand \bibinfo  [0]{\@secondoftwo}%
\providecommand \bibfield  [0]{\@secondoftwo}%
\providecommand \translation [1]{[#1]}%
\providecommand \BibitemOpen [0]{}%
\providecommand \bibitemStop [0]{}%
\providecommand \bibitemNoStop [0]{.\EOS\space}%
\providecommand \EOS [0]{\spacefactor3000\relax}%
\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
\let\auto@bib@innerbib\@empty
%</preamble>
\bibitem [{\citenamefont {Tagantsev}\ \emph {et~al.}(2018)\citenamefont
  {Tagantsev}, \citenamefont {Sherman}, \citenamefont {Astafiev}, \citenamefont
  {Venkatesh},\ and\ \citenamefont {Setter}}]{tagantsev_ferroelectric_2018}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~K.}\ \bibnamefont
  {Tagantsev}}, \bibinfo {author} {\bibfnamefont {V.~O.}\ \bibnamefont
  {Sherman}}, \bibinfo {author} {\bibfnamefont {K.~F.}\ \bibnamefont
  {Astafiev}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Venkatesh}},
  \ and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Setter}},\
  }\bibfield  {title} {\enquote {\bibinfo {title} {Ferroelectric {Materials}
  for {Microwave} {Tunable} {Applications}},}\ }\href@noop {} {\bibfield
  {journal} {\bibinfo  {journal} {J Electroceram}\ }\textbf {\bibinfo {volume}
  {11}},\ \bibinfo {pages} {5--66} (\bibinfo {year} {2018})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Vendik}\ \emph {et~al.}(1999)\citenamefont {Vendik},
  \citenamefont {Hollmann}, \citenamefont {Kozyrev},\ and\ \citenamefont
  {Prudan}}]{vendik_ferroelectric_1999}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
  {Vendik}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Hollmann}},
  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Kozyrev}}, \ and\
  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Prudan}},\ }\bibfield
  {title} {\enquote {\bibinfo {title} {Ferroelectric tuning of planar and bulk
  microwave devices},}\ }\href@noop {} {\bibfield  {journal} {\bibinfo
  {journal} {J. Supercond.}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo
  {pages} {325--338} (\bibinfo {year} {1999})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Lancaster}, \citenamefont {Powell},\ and\
  \citenamefont {Porch}(1998)}]{lancaster_thin-film_1998}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
  {Lancaster}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Powell}}, \
  and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Porch}},\ }\bibfield
   {title} {\enquote {\bibinfo {title} {Thin-film ferroelectric microwave
  devices},}\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
  {Supercond. Sci. Technol.}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo
  {pages} {1323} (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Xi}\ \emph {et~al.}(2000)\citenamefont {Xi},
  \citenamefont {Li}, \citenamefont {Si}, \citenamefont {Sirenko},
  \citenamefont {Akimov}, \citenamefont {Fox}, \citenamefont {Clark},\ and\
  \citenamefont {Hao}}]{xi_oxide_2000}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {X.}~\bibnamefont
  {Xi}}, \bibinfo {author} {\bibfnamefont {H.-C.}\ \bibnamefont {Li}}, \bibinfo
  {author} {\bibfnamefont {W.}~\bibnamefont {Si}}, \bibinfo {author}
  {\bibfnamefont {A.}~\bibnamefont {Sirenko}}, \bibinfo {author} {\bibfnamefont
  {I.}~\bibnamefont {Akimov}}, \bibinfo {author} {\bibfnamefont
  {J.}~\bibnamefont {Fox}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Clark}}, \ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Hao}},\
  }\bibfield  {title} {\enquote {\bibinfo {title} {Oxide thin films for tunable
  microwave devices},}\ }\href@noop {} {\bibfield  {journal} {\bibinfo
  {journal} {J. Electroceramics}\ }\textbf {\bibinfo {volume} {4}},\ \bibinfo
  {pages} {393--405} (\bibinfo {year} {2000})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Hand}\ and\ \citenamefont
  {Cummer}(2008)}]{hand_frequency_2008}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~H.}\ \bibnamefont
  {Hand}}\ and\ \bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont
  {Cummer}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Frequency
  tunable electromagnetic metamaterial using ferroelectric loaded split
  rings},}\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {J. Appl.
  Phys.}\ }\textbf {\bibinfo {volume} {103}},\ \bibinfo {pages} {066105}
  (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Zhao}\ \emph {et~al.}(2008)\citenamefont {Zhao},
  \citenamefont {Kang}, \citenamefont {Zhou}, \citenamefont {Zhao},
  \citenamefont {Li}, \citenamefont {Peng},\ and\ \citenamefont
  {Bai}}]{zhao_experimental_2008}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
  {Zhao}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Kang}}, \bibinfo
  {author} {\bibfnamefont {J.}~\bibnamefont {Zhou}}, \bibinfo {author}
  {\bibfnamefont {Q.}~\bibnamefont {Zhao}}, \bibinfo {author} {\bibfnamefont
  {L.}~\bibnamefont {Li}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
  {Peng}}, \ and\ \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Bai}},\
  }\bibfield  {title} {\enquote {\bibinfo {title} {Experimental demonstration
  of tunable negative phase velocity and negative refraction in a
  ferromagnetic/ferroelectric composite metamaterial},}\ }\href@noop {}
  {\bibfield  {journal} {\bibinfo  {journal} {Appl. Phys. Lett.}\ }\textbf
  {\bibinfo {volume} {93}},\ \bibinfo {pages} {201106} (\bibinfo {year}
  {2008})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Irvin}\ \emph {et~al.}(2005)\citenamefont {Irvin},
  \citenamefont {Levy}, \citenamefont {Guo},\ and\ \citenamefont
  {Bhalla}}]{irvin_three-dimensional_2005}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
  {Irvin}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Levy}},
  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Guo}}, \ and\ \bibinfo
  {author} {\bibfnamefont {A.}~\bibnamefont {Bhalla}},\ }\bibfield  {title}
  {\enquote {\bibinfo {title} {Three-dimensional polarization imaging of
  ({Ba},{Sr}){TiO}3:{MgO} composites},}\ }\href {\doibase 10.1063/1.1854722}
  {\bibfield  {journal} {\bibinfo  {journal} {Appl. Phys. Lett.}\ }\textbf
  {\bibinfo {volume} {86}},\ \bibinfo {pages} {042903} (\bibinfo {year}
  {2005})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Chung}\ \emph {et~al.}(2008)\citenamefont {Chung},
  \citenamefont {Elissalde}, \citenamefont {Maglione}, \citenamefont
  {Estournès}, \citenamefont {Paté},\ and\ \citenamefont
  {Ganne}}]{chung_low-losses_2008}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {U.-C.}\ \bibnamefont
  {Chung}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Elissalde}},
  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Maglione}}, \bibinfo
  {author} {\bibfnamefont {C.}~\bibnamefont {Estournès}}, \bibinfo {author}
  {\bibfnamefont {M.}~\bibnamefont {Paté}}, \ and\ \bibinfo {author}
  {\bibfnamefont {J.~P.}\ \bibnamefont {Ganne}},\ }\bibfield  {title} {\enquote
  {\bibinfo {title} {Low-losses, highly tunable {Ba}0.6sr0.4tio3 / {MgO}
  composite},}\ }\href {\doibase 10.1063/1.2837621} {\bibfield  {journal}
  {\bibinfo  {journal} {Appl. Phys. Lett.}\ }\textbf {\bibinfo {volume} {92}},\
  \bibinfo {pages} {042902} (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Wang}\ \emph {et~al.}(2012)\citenamefont {Wang},
  \citenamefont {Luo}, \citenamefont {Ni}, \citenamefont {Du}, \citenamefont
  {Li},\ and\ \citenamefont {Chen}}]{wang_piezoelectric_2012}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
  {Wang}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Luo}}, \bibinfo
  {author} {\bibfnamefont {F.}~\bibnamefont {Ni}}, \bibinfo {author}
  {\bibfnamefont {P.}~\bibnamefont {Du}}, \bibinfo {author} {\bibfnamefont
  {W.}~\bibnamefont {Li}}, \ and\ \bibinfo {author} {\bibfnamefont
  {H.}~\bibnamefont {Chen}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {Piezoelectric and ferroelectric properties of ({Bi}1- {xNa}0. 8k0. 2lax) 0.5
  {TiO}3 lead-free ceramics},}\ }\href {\doibase 10.1016/j.jallcom.2012.02.114}
  {\bibfield  {journal} {\bibinfo  {journal} {Journal of Alloys and Compounds}\
  }\textbf {\bibinfo {volume} {526}},\ \bibinfo {pages} {79--84} (\bibinfo
  {year} {2012})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Li}\ \emph {et~al.}(2013)\citenamefont {Li},
  \citenamefont {Lim}, \citenamefont {Yao}, \citenamefont {Tay},\ and\
  \citenamefont {Seah}}]{li_ferroelectric_2013}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {X.}~\bibnamefont
  {Li}}, \bibinfo {author} {\bibfnamefont {Y.-F.}\ \bibnamefont {Lim}},
  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Yao}}, \bibinfo {author}
  {\bibfnamefont {F.~E.~H.}\ \bibnamefont {Tay}}, \ and\ \bibinfo {author}
  {\bibfnamefont {K.~H.}\ \bibnamefont {Seah}},\ }\bibfield  {title} {\enquote
  {\bibinfo {title} {Ferroelectric {Poly}(vinylidene fluoride) {Homopolymer}
  {Nanotubes} {Derived} from {Solution} in {Anodic} {Alumina} {Membrane}
  {Template}},}\ }\href {\doibase 10.1021/cm3028466} {\bibfield  {journal}
  {\bibinfo  {journal} {Chem. Mater.}\ }\textbf {\bibinfo {volume} {25}},\
  \bibinfo {pages} {524--529} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Hu}\ \emph {et~al.}(2015)\citenamefont {Hu},
  \citenamefont {Gao}, \citenamefont {Kong}, \citenamefont {Yang},
  \citenamefont {Zhang}, \citenamefont {Liu}, \citenamefont {Zhang},\ and\
  \citenamefont {Sun}}]{hu_preparation_2015}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
  {Hu}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Gao}}, \bibinfo
  {author} {\bibfnamefont {J.}~\bibnamefont {Kong}}, \bibinfo {author}
  {\bibfnamefont {S.}~\bibnamefont {Yang}}, \bibinfo {author} {\bibfnamefont
  {Q.}~\bibnamefont {Zhang}}, \bibinfo {author} {\bibfnamefont
  {Z.}~\bibnamefont {Liu}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
  {Zhang}}, \ and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Sun}},\
  }\bibfield  {title} {\enquote {\bibinfo {title} {Preparation and dielectric
  properties of poly(vinylidene fluoride)/{Ba}0.6sr0.4tio3 composites},}\
  }\href {\doibase 10.1016/j.jallcom.2014.09.005} {\bibfield  {journal}
  {\bibinfo  {journal} {Journal of Alloys and Compounds}\ }\textbf {\bibinfo
  {volume} {619}},\ \bibinfo {pages} {686--692} (\bibinfo {year}
  {2015})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Sherman}\ \emph {et~al.}(2006)\citenamefont
  {Sherman}, \citenamefont {Tagantsev}, \citenamefont {Setter}, \citenamefont
  {Iddles},\ and\ \citenamefont
  {Price}}]{sherman_ferroelectric-dielectric_2006}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.~O.}\ \bibnamefont
  {Sherman}}, \bibinfo {author} {\bibfnamefont {A.~K.}\ \bibnamefont
  {Tagantsev}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Setter}},
  \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Iddles}}, \ and\ \bibinfo
  {author} {\bibfnamefont {T.}~\bibnamefont {Price}},\ }\bibfield  {title}
  {\enquote {\bibinfo {title} {Ferroelectric-dielectric tunable composites},}\
  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {J. Appl. Phys.}\
  }\textbf {\bibinfo {volume} {99}},\ \bibinfo {pages} {074104} (\bibinfo
  {year} {2006})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Jylha}\ and\ \citenamefont
  {Sihvola}(2008)}]{jylha_tunability_2008}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
  {Jylha}}\ and\ \bibinfo {author} {\bibfnamefont {A.~H.}\ \bibnamefont
  {Sihvola}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Tunability of
  granular ferroelectric dielectric composites},}\ }\href@noop {} {\bibfield
  {journal} {\bibinfo  {journal} {Prog. Electromagn. Res.}\ }\textbf {\bibinfo
  {volume} {78}},\ \bibinfo {pages} {189--207} (\bibinfo {year}
  {2008})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Sherman}, \citenamefont {Tagantsev},\ and\
  \citenamefont {Setter}(2004)}]{sherman_tunability_2004}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.~O.}\ \bibnamefont
  {Sherman}}, \bibinfo {author} {\bibfnamefont {A.~K.}\ \bibnamefont
  {Tagantsev}}, \ and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
  {Setter}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Tunability and
  loss of the ferroelectric-dielectric composites},}\ }in\ \href@noop {} {\emph
  {\bibinfo {booktitle} {14th {IEEE} {International} {Symposium} on
  {Applications} of {Ferroelectrics}, 2004. {ISAF}-04. 2004}}}\ (\bibinfo
  {year} {2004})\ pp.\ \bibinfo {pages} {33--38}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Astafiev}\ \emph {et~al.}(2003)\citenamefont
  {Astafiev}, \citenamefont {Sherman}, \citenamefont {Tagantsev},\ and\
  \citenamefont {Setter}}]{astafiev_can_2003}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.~F.}\ \bibnamefont
  {Astafiev}}, \bibinfo {author} {\bibfnamefont {V.~O.}\ \bibnamefont
  {Sherman}}, \bibinfo {author} {\bibfnamefont {A.~K.}\ \bibnamefont
  {Tagantsev}}, \ and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
  {Setter}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Can the addition
  of a dielectric improve the figure of merit of a tunable material?}}\
  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {J. Eur. Ceram.
  Soc.}\ }\textbf {\bibinfo {volume} {23}},\ \bibinfo {pages} {2381 -- 2386}
  (\bibinfo {year} {2003})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Okazaki}\ and\ \citenamefont
  {Nagata}(1973)}]{okazaki_effects_1973}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
  {Okazaki}}\ and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
  {Nagata}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Effects of
  {Grain} {Size} and {Porosity} on {Electrical} and {Optical} {Properties} of
  {PLZT} {Ceramics}},}\ }\href {\doibase 10.1111/j.1151-2916.1973.tb12363.x}
  {\bibfield  {journal} {\bibinfo  {journal} {J. Am. Ceram. Soc.}\ }\textbf
  {\bibinfo {volume} {56}},\ \bibinfo {pages} {82--86} (\bibinfo {year}
  {1973})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Stanculescu}\ \emph {et~al.}(2015)\citenamefont
  {Stanculescu}, \citenamefont {Ciomaga}, \citenamefont {Padurariu},
  \citenamefont {Galizia}, \citenamefont {Horchidan}, \citenamefont {Capiani},
  \citenamefont {Galassi},\ and\ \citenamefont
  {Mitoseriu}}]{stanculescu_study_2015}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
  {Stanculescu}}, \bibinfo {author} {\bibfnamefont {C.~E.}\ \bibnamefont
  {Ciomaga}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Padurariu}},
  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Galizia}}, \bibinfo
  {author} {\bibfnamefont {N.}~\bibnamefont {Horchidan}}, \bibinfo {author}
  {\bibfnamefont {C.}~\bibnamefont {Capiani}}, \bibinfo {author} {\bibfnamefont
  {C.}~\bibnamefont {Galassi}}, \ and\ \bibinfo {author} {\bibfnamefont
  {L.}~\bibnamefont {Mitoseriu}},\ }\bibfield  {title} {\enquote {\bibinfo
  {title} {Study of the role of porosity on the functional properties of
  ({Ba},{Sr}){TiO}3 ceramics},}\ }\href {\doibase
  10.1016/j.jallcom.2015.03.252} {\bibfield  {journal} {\bibinfo  {journal} {J.
  Alloys Compd.}\ }\textbf {\bibinfo {volume} {643}},\ \bibinfo {pages}
  {79--87} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Padurariu}\ \emph
  {et~al.}(2012{\natexlab{a}})\citenamefont {Padurariu}, \citenamefont
  {Curecheriu}, \citenamefont {Galassi},\ and\ \citenamefont
  {Mitoseriu}}]{padurariu_tailoring_2012}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
  {Padurariu}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
  {Curecheriu}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Galassi}},
  \ and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Mitoseriu}},\
  }\bibfield  {title} {\enquote {\bibinfo {title} {Tailoring non-linear
  dielectric properties by local field engineering in anisotropic porous
  ferroelectric structures},}\ }\href {\doibase 10.1063/1.4729878} {\bibfield
  {journal} {\bibinfo  {journal} {Appl Phys Lett}\ }\textbf {\bibinfo {volume}
  {100}},\ \bibinfo {pages} {252905} (\bibinfo {year}
  {2012}{\natexlab{a}})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Padurariu}\ \emph
  {et~al.}(2012{\natexlab{b}})\citenamefont {Padurariu}, \citenamefont
  {Curecheriu}, \citenamefont {Buscaglia},\ and\ \citenamefont
  {Mitoseriu}}]{padurariu_field-dependent_2012}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
  {Padurariu}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
  {Curecheriu}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
  {Buscaglia}}, \ and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
  {Mitoseriu}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {Field-dependent permittivity in nanostructured {BaTiO}\$\{\}\_\{3\}\$
  ceramics: {Modeling} and experimental verification},}\ }\href {\doibase
  10.1103/PhysRevB.85.224111} {\bibfield  {journal} {\bibinfo  {journal} {Phys
  Rev B}\ }\textbf {\bibinfo {volume} {85}},\ \bibinfo {pages} {224111}
  (\bibinfo {year} {2012}{\natexlab{b}})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Cazacu}\ \emph {et~al.}(2013)\citenamefont {Cazacu},
  \citenamefont {Curecheriu}, \citenamefont {Neagu}, \citenamefont {Padurariu},
  \citenamefont {Cernescu}, \citenamefont {Lisiecki},\ and\ \citenamefont
  {Mitoseriu}}]{cazacu_tunable_2013}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Cazacu}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Curecheriu}},
  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Neagu}}, \bibinfo
  {author} {\bibfnamefont {L.}~\bibnamefont {Padurariu}}, \bibinfo {author}
  {\bibfnamefont {A.}~\bibnamefont {Cernescu}}, \bibinfo {author}
  {\bibfnamefont {I.}~\bibnamefont {Lisiecki}}, \ and\ \bibinfo {author}
  {\bibfnamefont {L.}~\bibnamefont {Mitoseriu}},\ }\bibfield  {title} {\enquote
  {\bibinfo {title} {Tunable gold-chitosan nanocomposites by local field
  engineering},}\ }\href {\doibase 10.1063/1.4809673} {\bibfield  {journal}
  {\bibinfo  {journal} {Appl Phys Lett}\ }\textbf {\bibinfo {volume} {102}},\
  \bibinfo {pages} {222903} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Carignan}\ \emph {et~al.}(2011)\citenamefont
  {Carignan}, \citenamefont {Yelon}, \citenamefont {Menard},\ and\
  \citenamefont {Caloz}}]{carignan_ferromagnetic_2011}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
  {Carignan}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Yelon}},
  \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Menard}}, \ and\ \bibinfo
  {author} {\bibfnamefont {C.}~\bibnamefont {Caloz}},\ }\bibfield  {title}
  {\enquote {\bibinfo {title} {Ferromagnetic {Nanowire} {Metamaterials}:
  {Theory} and {Applications}},}\ }\href {\doibase 10.1109/TMTT.2011.2163202}
  {\bibfield  {journal} {\bibinfo  {journal} {IEEE Trans. Microw. Theory
  Tech.}\ }\textbf {\bibinfo {volume} {59}},\ \bibinfo {pages} {2568--2586}
  (\bibinfo {year} {2011})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Werner}\ \emph {et~al.}(2007)\citenamefont {Werner},
  \citenamefont {Kwon}, \citenamefont {Khoo}, \citenamefont {Kildishev},\ and\
  \citenamefont {Shalaev}}]{werner_liquid_2007}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~H.}\ \bibnamefont
  {Werner}}, \bibinfo {author} {\bibfnamefont {D.-H.}\ \bibnamefont {Kwon}},
  \bibinfo {author} {\bibfnamefont {I.-C.}\ \bibnamefont {Khoo}}, \bibinfo
  {author} {\bibfnamefont {A.~V.}\ \bibnamefont {Kildishev}}, \ and\ \bibinfo
  {author} {\bibfnamefont {V.~M.}\ \bibnamefont {Shalaev}},\ }\bibfield
  {title} {\enquote {\bibinfo {title} {Liquid crystal clad near-infrared
  metamaterials with tunable negative-zero-positive refractive indices},}\
  }\href {\doibase 10.1364/OE.15.003342} {\bibfield  {journal} {\bibinfo
  {journal} {Opt. Express, OE}\ }\textbf {\bibinfo {volume} {15}},\ \bibinfo
  {pages} {3342--3347} (\bibinfo {year} {2007})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Keiser}\ and\ \citenamefont
  {Klarskov}(2019)}]{keiser_terahertz_2019}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~R.}\ \bibnamefont
  {Keiser}}\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
  {Klarskov}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Terahertz
  {Field} {Confinement} in {Nonlinear} {Metamaterials} and {Near}-{Field}
  {Imaging}},}\ }\href {\doibase 10.3390/photonics6010022} {\bibfield
  {journal} {\bibinfo  {journal} {Photonics}\ }\textbf {\bibinfo {volume}
  {6}},\ \bibinfo {pages} {22} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Fan}\ \emph {et~al.}(2013)\citenamefont {Fan},
  \citenamefont {Hwang}, \citenamefont {Liu}, \citenamefont {Strikwerda},
  \citenamefont {Sternbach}, \citenamefont {Zhang}, \citenamefont {Zhao},
  \citenamefont {Zhang}, \citenamefont {Nelson},\ and\ \citenamefont
  {Averitt}}]{fan_nonlinear_2013}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
  {Fan}}, \bibinfo {author} {\bibfnamefont {H.~Y.}\ \bibnamefont {Hwang}},
  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Liu}}, \bibinfo {author}
  {\bibfnamefont {A.~C.}\ \bibnamefont {Strikwerda}}, \bibinfo {author}
  {\bibfnamefont {A.}~\bibnamefont {Sternbach}}, \bibinfo {author}
  {\bibfnamefont {J.}~\bibnamefont {Zhang}}, \bibinfo {author} {\bibfnamefont
  {X.}~\bibnamefont {Zhao}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont
  {Zhang}}, \bibinfo {author} {\bibfnamefont {K.~A.}\ \bibnamefont {Nelson}}, \
  and\ \bibinfo {author} {\bibfnamefont {R.~D.}\ \bibnamefont {Averitt}},\
  }\bibfield  {title} {\enquote {\bibinfo {title} {Nonlinear {Terahertz}
  {Metamaterials} via {Field}-{Enhanced} {Carrier} {Dynamics} in {GaAs}},}\
  }\href {\doibase 10.1103/PhysRevLett.110.217404} {\bibfield  {journal}
  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {110}},\
  \bibinfo {pages} {217404} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Allaire}(1992)}]{allaire_homogenization_1992}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
  {Allaire}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Homogenization
  and {Two}-{Scale} {Convergence}},}\ }\href@noop {} {\bibfield  {journal}
  {\bibinfo  {journal} {SIAM J. Math. Anal.}\ }\textbf {\bibinfo {volume}
  {23}},\ \bibinfo {pages} {1482--1518} (\bibinfo {year} {1992})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Guenneau}\ and\ \citenamefont
  {Zolla}(2000)}]{guenneau_homogenization_2000}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Guenneau}}\ and\ \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
  {Zolla}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Homogenization of
  {Three}-{Dimensional} {Finite} {Photonic} {Crystals}},}\ }\href@noop {}

>>>>

\documentclass[%
 aip,
% jmp,
% bmf,
% sd,
% rsi,
 amsmath,amssymb,
%preprint,%
 reprint,%
%author-year,%
%author-numerical,%
% Conference Proceedings
linenumbers
]{revtex4-1}

@@

\usepackage{xcolor}
\definecolor{correction}{HTML}{de5e5e}
\newcommand{\co}[1]{\textcolor{correction}{#1}}

%
\usepackage[outdir=./]{epstopdf}
\graphicspath{{./}{../../data/figures/}}

@@

% \bibliographystyle{RS}
\bibliography{../biblio}
